This is the title [Article v\versionnumber]

### 2022-03-16 manuscript/manuscript.tex
Add more tutorial text, switch to lstlistings
* dont use the code environment any more, use lstlistings instead
* split subsection: Running MD for GIST and Running the GIST analysis

@@

\newenvironment{code}{\par \noindent \ttfamily \ignorespaces}{\par}

@@

\subsection{Streptavidin/Biotin}
\subsection{Tutorial data}
We will use the 1STP crystal structure to start our calculations.
For the sake of simplicity, you can download prepared and solvated Amber topologies and structures based on 1STP by running
\begin{code}
git clone git@github.com:liedllab/gist-tutorial.git
\end{code}
This will download the tutorial files (including both the manuscript and the examples in the \software{code} folder).
\subsection{System Preparation and Equilibration}
If you want to skip this section, run 
\begin{code}
	make equilibration-targets
\end{code}
in the code folder. This assumes that you have Python and Amber set up properly and that \software{pmemd.cuda} is in the PATH.

@@

Here, we choose not to include any sampling of the conformational states. 
It is therefore important that the conformations of the monomers in the complex and dissociated states match exactly. 
We provide a script called \software{cpptraj\_remove\_mol.sh} that removes a single molecule from a topology and structure using \software{cpptraj} without altering the rest of the system. \todo{Explain cpptraj rather than our script. The script is for the automated workflow only.}

@@

\subsection{Running GIST}

@@

\subsection{Visualizing $\dgsolv$}
\subsection{Contribution of Hydration to Binding}

>>>>

\usepackage{listings}

@@

\lstdefinestyle{code}{
	basicstyle=\ttfamily
}
\lstset{style=code}

@@

\subsection{Streptavidin/Biotin}
\subsection{Tutorial data}
We will use the 1STP crystal structure to start our calculations.
For the sake of simplicity, you can download prepared and solvated Amber topologies and structures based on 1STP by running
\begin{lstlisting}
git clone git@github.com:liedllab/gist-tutorial.git
\end{lstlisting}
This will download the tutorial files (including both the manuscript and the examples in the \software{code} folder).
\subsection{System Preparation and Equilibration}
If you want to skip this section, run 
\begin{lstlisting}
make equilibration-targets
\end{lstlisting}
in the code folder. This assumes that you have Python and Amber set up properly and that \software{pmemd.cuda} is in the PATH.

@@

Here, we choose not to include any sampling of the conformational states. 
It is therefore important that the conformations of the monomers in the complex and dissociated states match exactly. 
Use \software{cpptraj} to produce biotin and streptavidin structures based on the complex by stripping the respective other molecule like this:
\begin{lstlisting}
parm complex/solvated.parm7
trajin complex/equil/EQUIL-DONE.rst
strip ^2 parmout streptavidin/solvated.parm7
trajout streptavidin/pre-equil.ncrst
\end{lstlisting}
(Adapt for biotin as necessary.)

%We provide a script called \software{cpptraj\_remove\_mol.sh} that removes a single molecule from a topology and structure using \software{cpptraj} without altering the rest of the system. \todo{Explain cpptraj rather than our script. The script is for the automated workflow only.}

@@

\subsection{Running MD for GIST}

@@

An example Amber input file for GIST might look like this:
\begin{lstlisting}

\end{lstlisting}
\subsection{Running the GIST analysis}

For easier post-processing, we will use grids that contain the whole molecule.
This could in theory be avoided for streptavidin and the complex, since only the surrounding of the biotin molecule (i.e., the binding pocket) is required for the analysis.
We also recommend that you center the molecule in space.
For each system (biotin, streptavidin, complex), produce a centered pdb file using \software{cpptraj}:
\begin{lstlisting}
parm ../solvated.parm7
trajin EQUIL-DONE.rst
autoimage !(:WAT) origin
strip :WAT
trajout equil-centered.pdb
\end{lstlisting}
Then, find the extent (minimum and maximum) of the x-, y-, and z-coordinates for each system.
This can be done e.g., using the \software{mdtraj} package in Python.
\begin{lstlisting}[basicstyle=\ttfamily]
import mdtraj as md
pdb = md.load("equil-centered.pdb")
min = pdb.xyz[0].min(0) * 10.
max = pdb.xyz[0].max(0) * 10.
print(*list(zip("xyz", min, max)), sep="\n")
\end{lstlisting}
Then, decide on grid dimensions for every system.
For a system centered at the origin with a spacing of \SI{0.5}{\angstrom} and a buffer of, e.g., \SI{7}{\angstrom} between the solute and the grid wall, you need $4.0\times (d+7)$ bins in the respective direction, where $d$ is the larger of $-$min and $+$max in the respective direction.
\subsection{Visualizing $\dgsolv$}
\subsection{Contribution of Hydration to Binding}
